---
title: "Live Session Unit 11 Assignment"
author: "Chris Irwin"
date: "11/16/2016"
output: html_document
---

```{r setup, include=FALSE}
library(fpp)
```

###I was assigned the hSales data set, which is included in the FPP package from r

####Question A
```{r}
#create new data frame
sales <- hsales
	
#plot hsales data
plot(hsales)
```

#####Overall you can see that there is a seasonal trend that creates high and lows at what looks to be similar intervals


####Question B
#####Create Classical Decomposition
```{r}
#Get the classic decomposition
fitClassic <- decompose(sales)

#Plot data 
plot(sales, col="dark gray") + lines(fitClassic$trend, col = "red")
```

####Question C
#####Yes, if you overlay the classic trend you will see that overall it is a very poor fit to the data. 

####Question D
#####Create Seasonal Adjustment
```{r}
#need to see what the seasonal adjustment looks like
	fitSeason <- seasadj(fitClassic)

	#Plot seasonal data 
	plot(sales, col=" dark green") + lines(fitSeason, col = "red")
```

####Question E
```{r}
#create data frame for outlier update
salesWOutlier <- hsales
	
#Update data frame with outlier 
salesWOutlier[274] <- 500

#Decompose outlier data
fitClassicWOutlier <- decompose(salesWOutlier)

#Seasonalize the Outlier data
fitSeasonWOutlier <- seasadj(fitClassicWOutlier)

#Plot seasonal data 
plot(sales, col=" dark Blue") + lines(fitSeasonWOutlier, col = "red")
```
#####The Outlier creates a large spike in the data and then quickly comes back to the model over all. 

####Question F
#####Overall where ever you add the value there will be a large spike, but it looks to regain its fit relatively quickly
#####this would leave me to believe it has little effect, especially when it is used in a seasonality model.

####Question G
```{r}
#Create STL Decomp data
fitSTL <- stl(sales, s.window = 5)

#Plot STL trend line vs Sales
plot(sales, col="dark grey") + lines(fitSTL$time.series[,2], col = "red")
```



